### 2021-04-08 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsubsection{Information Flow Check}
\tool{} is designed to help software developers find and understand the side-channel vulnerabilities. To ease the procedure of fixing the bug, we also track the information flow for each byte of the input
buffer.
The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
At the beginning of the analysis, \tool{} keep a track for each byte in
the original buffer. When \tool{} symbolically executes each instruction in the trace, it will check every value read from registers or memory. If the value is concrete, it means the instruction has nothing to do with the original buffer.
If the value is a formula, it means the original information passes through the instruction. Since each byte in the sensitive buffer is represented as a symbol with a unique ID, \tool{} can know which byte in the origin buffer goes through the instruction.

@@

During our evaluation process, we are interested in the following
aspects:
\begin{enumerate}
    \item Is \tool{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
    \item How much performance overhead does the method introduce? (Performance)
    \item How effective are the design choices made by the tool method? (Design Choices)
\end{enumerate}

@@

    Total              &                          & 913               & 241               & 672            & 167,155,052 & 341m            \\\hline
  \end{tabular}
\end{table*}
Table~\ref{table:over_result} summarizes the results.
\tool{} finds 913 leaks in the crypto libraries.
Among these 913 leaks, 241 are due to secret-dependent
control-flow transfers and 672 are due to secret-dependent data accesses.

@@

In this section, we compare \tool{} with the
existing trace-based side-channel detection tools on vulnerability detections. For other tools, we use the data in the paper. As other tools do not quantify leakage sites, we only include the time of detecting vulnerabilities to perform a fair comparison.

The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. Under the circumstance, we think it is only a leakage.
We have confirmed that \tool{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \tool{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \tool{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours to process
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While those optimizations do not introduce false positives, they may miss some
vulnerabilities.
Third, CacheD only symbolizes the encryption keys. Some side-channel leakages when the input messages equal to some certain values. It is possible that CacheD miss some
leakages as we have discussion the previous sections.
We notice that the number of instructions in those traces are different due to the different analysis starting functions and building options during the evaluation.
Table~\ref{eval:cacheD} shows that
\tool{} is faster than CacheD. \tool{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\tool{} on AES from OpenSSL
0.9.7, \tool{} is over 100x faster than CacheD.
\begin{table*}[]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}

@@

DATA~\cite{217537} identifies
side-channel leakages by finding differences in execution traces of
the test program under \emph{various secret inputs}. According to
the original DATA paper, it uses 443 different traces to analyze the
side-channel vulnerabilities in symmetric cyphers and 450 different
traces to analyze the side-channel vulnerabilities in asymmetric
cyphers. On the other hand, \tool{} detects side-channel
vulnerabilities from one execution trace. \tool{} uses symbolic
analysis to extract formulas that model each side-channel
leakage. After that, we sample the formula with \emph{various
  secret inputs} to detect and quantify each leakage site. In
theory, DATA might have better code coverage than \tool{} because it
uses more execution traces,  but \tool{} has the following
advantages. a) \tool{} is faster than DATA. For example, it takes
116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@. \tool{} only spends 34 minutes, as shown in Table~\ref{table:over_result}. It takes 13 minutes and 20 minutes
for DATA to analyze the side-channel leakages in AES and DES,
respectively. On the other hand, \tool{} finishes its analysis in
less than ten seconds while finding all the leakages reported by
DATA. b) Because \tool{} does not run the test program again when wedinghao w
have a new \emph{secret input}, \tool{} can test more input secrets
on those formulas within the same time to achieve better precision.
c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
The strength of Abacus is that it does not need such domain knowledge.
DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
\tool{} finds the vulnerability.  For each leakage site, \tool{} can provide
concrete examples to trigger the issue and give an estimation to
assess the severity level of the vulnerability.

\subsection{Case Studies}
\subsubsection{DES and AES}
Our tool confirms that both implementations in OpenSSL and mbedTLS have side-channel leakages
sites. Moreover, we find that all the leakages belong to the secret-dependent data accesses. The reference implementation of AES uses four lookup tables to speed up the computation. However, such implementation are vulnerable to side-channel attacks. Previous work has shown an end-to-end attack to fully recover the key. Our findings is similar to the previous work. We also notice that later version of OpenSSL (after 1.0.1) uses a modified version with smaller S-table. However, \tool{} also find the leakage sites in the version. Recent work also finds the sites through theoretical analysis.

\subsubsection{RSA}
We also evaluates our tool on the RSA implementations. With the optimizations
introduced in the previous section, we do not apply any domain knowledge to
simplify the analysis. Therefore, our tools can identify all the leakage sites
reported by CacheD~\cite{203878} in a shorter time. Our tool finds that most
leakages in RSA occur in the big number implementation. We also find the newer
versions of RSA in OpenSSL tend to have fewer leakages detected by \tool{}.

Even for the up-to-date version of OpenSSL, \tool{} still find several
side-channel leakages. Figure~\ref{chapter3:fig:unknown_leakage} shows an unknown leakage site in OpenSSL 1.1.1. It is a secret-dependent control flow transfers. 
However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.

@@

\subsubsection{Monocypher}\label{eval:mono}
Monocypher is a small, easy to use cryptographic library with
performance comparable to LibSodium~\cite{libsodium} and NaCl~\cite{bernstein2012security}.
We choose four ciphers that are
designed to be side-channel resistant from the library.
Because those ciphers have no
data flow from secrets to branch conditions and load addresses.
Monocypher should be safe under our threat models.
We analyze those ciphers with \tool{}, and it reports no leaks.
This indicates that \tool{} is effective for validating countermeasures.

@@

\tool{} works on native x86 execution traces. The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has the common limitations of dynamic approaches. \tool{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs. Our evaluation also confirms the above point. For symmetric encryption, during our evaluation there is no secret-dependent control-flow transfers. RSA implementations have several secret-dependent control-flow transfers. Most of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. For RSA, the latest OpenSSL only has one leakage site that can leak more than 3 bits while there are 22 leakage sites according to \tool{}. DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. The sampling method  seems simple and may miss some leakages in theory. However, the evaluation result shows \tool{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

>>>>

\subsubsection{Information Flow Check}
\detect{} is designed to help software developers find and understand the side-channel vulnerabilities. To ease the procedure of fixing the bug, we also track the information flow for each byte of the input
buffer.
The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
At the beginning of the analysis, \detect{} keep a track for each byte in
the original buffer. When \detect{} symbolically executes each instruction in the trace, it will check every value read from registers or memory. If the value is concrete, it means the instruction has nothing to do with the original buffer.
If the value is a formula, it means the original information passes through the instruction. Since each byte in the sensitive buffer is represented as a symbol with a unique ID, \detect{} can know which byte in the origin buffer goes through the instruction.

@@

During our evaluation process, we are interested in the following
aspects:
\begin{enumerate}
    \item Is \detect{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
    \item How much performance overhead does the method introduce? (Performance)
    \item How effective are the design choices made by the tool method? (Design Choices)
\end{enumerate}

@@

    Total              &                          & 913               & 241               & 672            & 167,155,052 & 341m            \\\hline
  \end{tabular}
\end{table*}
Table~\ref{table:over_result} summarizes the results.
\detect{} finds 913 leaks in the crypto libraries.
Among these 913 leaks, 241 are due to secret-dependent
control-flow transfers and 672 are due to secret-dependent data accesses.

@@

In this section, we compare \detect{} with the
existing trace-based side-channel detection tools on vulnerability detections. For other tools, we use the data in the paper. As other tools do not quantify leakage sites, we only include the time of detecting vulnerabilities to perform a fair comparison.

The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. Under the circumstance, we think it is only a leakage.
We have confirmed that \detect{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \detect{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \detect{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours to process
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While those optimizations do not introduce false positives, they may miss some
vulnerabilities.
Third, CacheD only symbolizes the encryption keys. Some side-channel leakages when the input messages equal to some certain values. It is possible that CacheD miss some
leakages as we have discussion the previous sections.
We notice that the number of instructions in those traces are different due to the different analysis starting functions and building options during the evaluation.
Table~\ref{eval:cacheD} shows that
\detect{} is faster than CacheD. \detect{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\detect{} on AES from OpenSSL
0.9.7, \detect{} is over 100x faster than CacheD.
\begin{table*}[]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}

@@

DATA~\cite{217537} identifies
side-channel leakages by finding differences in execution traces of
the test program under \emph{various secret inputs}. According to
the original DATA paper, it uses 443 different traces to analyze the
side-channel vulnerabilities in symmetric cyphers and 450 different
traces to analyze the side-channel vulnerabilities in asymmetric
cyphers. On the other hand, \detect{} detects side-channel
vulnerabilities from one execution trace. \detect{} uses symbolic
analysis to extract formulas that model each side-channel
leakage. After that, we sample the formula with \emph{various
  secret inputs} to detect and quantify each leakage site. In
theory, DATA might have better code coverage than \detect{} because it
uses more execution traces,  but \detect{} has the following
advantages. a) \detect{} is faster than DATA. For example, it takes
116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@. \detect{} only spends 34 minutes, as shown in Table~\ref{table:over_result}. It takes 13 minutes and 20 minutes
for DATA to analyze the side-channel leakages in AES and DES,
respectively. On the other hand, \detect{} finishes its analysis in
less than ten seconds while finding all the leakages reported by
DATA. b) Because \detect{} does not run the test program again when wedinghao w
have a new \emph{secret input}, \detect{} can test more input secrets
on those formulas within the same time to achieve better precision.
c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
The strength of Abacus is that it does not need such domain knowledge.
DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
\detect{} finds the vulnerability.  For each leakage site, \detect{} can provide
concrete examples to trigger the issue and give an estimation to
assess the severity level of the vulnerability.

\subsection{Case Studies}
\subsubsection{DES and AES}
Our tool confirms that both implementations in OpenSSL and mbedTLS have side-channel leakages
sites. Moreover, we find that all the leakages belong to the secret-dependent data accesses. The reference implementation of AES uses four lookup tables to speed up the computation. However, such implementation are vulnerable to side-channel attacks. Previous work has shown an end-to-end attack to fully recover the key. Our findings is similar to the previous work. We also notice that later version of OpenSSL (after 1.0.1) uses a modified version with smaller S-table. However, \detect{} also find the leakage sites in the version. Recent work also finds the sites through theoretical analysis.

\subsubsection{RSA}
We also evaluates our tool on the RSA implementations. With the optimizations
introduced in the previous section, we do not apply any domain knowledge to
simplify the analysis. Therefore, our tools can identify all the leakage sites
reported by CacheD~\cite{203878} in a shorter time. Our tool finds that most
leakages in RSA occur in the big number implementation. We also find the newer
versions of RSA in OpenSSL tend to have fewer leakages detected by \detect{}.

Even for the up-to-date version of OpenSSL, \detect{} still find several
side-channel leakages. Figure~\ref{chapter3:fig:unknown_leakage} shows an unknown leakage site in OpenSSL 1.1.1. It is a secret-dependent control flow transfers. 
However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.

@@

\subsubsection{Monocypher}\label{eval:mono}
Monocypher is a small, easy to use cryptographic library with
performance comparable to LibSodium~\cite{libsodium} and NaCl~\cite{bernstein2012security}.
We choose four ciphers that are
designed to be side-channel resistant from the library.
Because those ciphers have no
data flow from secrets to branch conditions and load addresses.
Monocypher should be safe under our threat models.
We analyze those ciphers with \detect{}, and it reports no leaks.
This indicates that \detect{} is effective for validating countermeasures.

@@

\detect{} works on native x86 execution traces. The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has the common limitations of dynamic approaches. \detect{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs. Our evaluation also confirms the above point. For symmetric encryption, during our evaluation there is no secret-dependent control-flow transfers. RSA implementations have several secret-dependent control-flow transfers. Most of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. For RSA, the latest OpenSSL only has one leakage site that can leak more than 3 bits while there are 22 leakage sites according to \detect{}. DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. The sampling method  seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

  \item We implement the above method in a tool called \tool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \tool{} can help developers fix the reported vulnerabilities.
\end{itemize}

@@

@@

Considering the example in figure~\ref{fig:align}, it read the data from the array \textsf{T} based on the index (i). If the index (i) is associated with a key, it could be a side-channel vulnerability. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated in different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, because the based address is different. So we get two different memory accesses. Under the circumstance, it is a false positive. Besides, it can cause false negatives as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different index. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \tool{} can not observe the difference here, which can cause a false positive.

@@

\section{Design}
In this section, we explain the implementation of \tool{}.
we first present the overview of \tool{}. After that, we discuss some design details to implement \tool{}.

\subsection{Overview}
Figure~\ref{fig:workflow} shows an overview of our side-channel leakages quantification tool. Given the source code of the victim program, \tool{} can find the address-based side-channel leakages by fuzzing the victim program. To assist the illustration, we divide the workflow of ~\tool{} into three steps. For the first step, we build the target program from the source code. After that, we give them random inputs to the victim program and run the target program and record each of the address in the binary file is hit or not and store the information in a bitmap. Next, we analyze the side-channel leakage from the address access bitmap. We split the address space into several segments to speed up the comparison according to Meta information. Finally, \tool{} Generate the final leakage report. For each leakage sites, \tool{} gives the conservative estimation of the information leakage. Every leakage site in the report is a true leakage and there is no false positives.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
  \caption{The workflow of \tool{}. We try to divide the \tool{} into three steps to assist the illustration. }\label{fig:workflow}
\end{figure}

@@

\subsubsection{Various Granularities Side-channel Detection}
\tool{} can detect the side-channel vulnerabilities in different granularity. For each granularity, we calculate a new bitmap that represents access information of each unit. We have the bitmap of the memory access at the byte level. An attacker who has the coarse-grained observation at address space may not be able to distinguish the address difference. For example, modern X64 computer system uses 48-bit virtual memory addresses. The top 36 bit of the virtual address is called Virtual Page Number (VPN) and the bottom 12 bits of the virtual address is called offset. The memory management unit (MMU) transfer the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keep the offset of the address. So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the the page-level observation.

@@

\section{Implementation}
We have implemented a prototype of \tool{}. It takes an input of ELF binary as well as the source code of the corresponding problem. The front-end of \tool{} is implemented in Python. It can generate random inputs and test the program with those inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses libelfin, an open source library to parse ELF binaries and read DWARF debug information. The current implementation can support both 64-bits and 32-bits ELF binary in Linux. \tool{} will be open-sourced.

@@

This paper presents an approach that tries to give the conservative estimate of the amount of leaked information by address-based side-channel attacks. Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses. Despite those kinds of side-channel leakages have been discovered for decades, the up-to-date software still has some side channel leakages. For some of those vulnerabilities, developers don't fix them because they think those side-channel vulnerabilities are not important. To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability. However, demonstrating an end-to-end attack often need a lots of manual efforts and the domain knowledge of the victim program, which is not often the case in practices. It is good to have a tool that can assess the severity level of those side channel leakages automatically. So it would be better to have a proper metric to quantify the side-channel leakage. However, we find previous side-channel quantification tools are developed to  ensure the noninterference of the program. They use over approximation heuristics method to quantify the leakage. For example, CacheAudit estimate that a 128-bit AES encryption can leaks more than 128 bits. As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.

@@

\tool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \tool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs. For other libraries like graphic rendering, machine learning, \tool{} is very likely to miss some side-channel vulnerabilities. However, \tool{} is not designed to find side-channel vulnerabilities. The goal of \tool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is a main limitation of \tool{}. However, users of \tool{} should be aware the code coverage problem.

Another limitation is that \tool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks. Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input. At line 3, it calculate an index based on the value of the secret. Depending on the value of index, it may or may not run the code at line 6. So line 5 is the reason that causes the vulnerability. But \tool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.

>>>>

  \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}

@@

\subsection{Chi-squared Test}

@@

Considering the example in figure~\ref{fig:align}, it read the data from the array \textsf{T} based on the index (i). If the index (i) is associated with a key, it could be a side-channel vulnerability. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated in different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, because the based address is different. So we get two different memory accesses. Under the circumstance, it is a false positive. Besides, it can cause false negatives as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different index. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ can not observe the difference here, which can cause a false positive.

@@

\section{Multiple Leakages Sites}

\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

\subsection{Overview}
Figure~\ref{fig:workflow} shows an overview of our side-channel leakages quantification tool. Given the source code of the victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program. To assist the illustration, we divide the workflow of ~\ctool{} into three steps. For the first step, we build the target program from the source code. After that, we give them random inputs to the victim program and run the target program and record each of the address in the binary file is hit or not and store the information in a bitmap. Next, we analyze the side-channel leakage from the address access bitmap. We split the address space into several segments to speed up the comparison according to Meta information. Finally, \ctool{} Generate the final leakage report. For each leakage sites, \ctool{} gives the conservative estimation of the information leakage. Every leakage site in the report is a true leakage and there is no false positives.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
  \caption{The workflow of \ctool{}. We try to divide the \ctool{} into three steps to assist the illustration. }\label{fig:workflow}
\end{figure}

@@

\subsubsection{Various Granularities Side-channel Detection}
\ctool{} can detect the side-channel vulnerabilities in different granularity. For each granularity, we calculate a new bitmap that represents access information of each unit. We have the bitmap of the memory access at the byte level. An attacker who has the coarse-grained observation at address space may not be able to distinguish the address difference. For example, modern X64 computer system uses 48-bit virtual memory addresses. The top 36 bit of the virtual address is called Virtual Page Number (VPN) and the bottom 12 bits of the virtual address is called offset. The memory management unit (MMU) transfer the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keep the offset of the address. So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the the page-level observation.

@@

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding problem. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with those inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses libelfin, an open source library to parse ELF binaries and read DWARF debug information. The current implementation can support both 64-bits and 32-bits ELF binary in Linux. \ctool{} will be open-sourced.

\section{Evaluation}

@@

This paper presents an approach that tries to give the conservative estimate of the amount of leaked information by address-based side-channel attacks. Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses. Despite those kinds of side-channel leakages have been discovered for decades, the up-to-date software still has some side channel leakages. For some of those vulnerabilities, developers don't fix them because they think those side-channel vulnerabilities are not important. To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability. However, demonstrating an end-to-end attack often need a lots of manual efforts and the domain knowledge of the victim program, which is not often the case in practices. It is good to have a tool that can assess the severity level of those side channel leakages automatically. So it would be better to have a proper metric to quantify the side-channel leakage. However, we find previous side-channel quantification tools are developed to  ensure the noninterference of the program. They use over approximation heuristics method to quantify the leakage. For example, CacheAudit estimates that a 128-bit AES encryption can leaks more than 128 bits. As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.

@@

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs. For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find side-channel vulnerabilities. The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is a main limitation of \ctool{}. However, users of \ctool{} should be aware the code coverage problem.

Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks. Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input. At line 3, it calculate an index based on the value of the secret. Depending on the value of index, it may or may not run the code at line 6. So line 5 is the reason that causes the vulnerability. But \ctool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.

### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

In Chapter~\ref{chapter3}, we present the first technique \detect{}.

>>>>

In Chapter~\ref{chapter3}, we present a practical address-based side-channel detection tool, \detect{}, that is capable of detecting

In Chapter~\ref{chapter4}, we present a novel method to quantify address-based side-channel leakage. We implement the method in a prototype called \tool{} and show its effectiveness in finding and quantifying side-channel leakage. With the new definition of information leakage that models actual side-channel attackers, quantifying the number of leaked bits helps understand the severity level of side-channel vulnerabilities. The evaluation confirms that \tool{} is useful in estimating the amount of leaked information in real-world applications.

In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically. The proposed method can produce the conservative estimation of the side-channel leakage of the deterministic program. As a result, any severe leakage reported by \ctool{} is the true severe leakage. Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.
